Two-Dimensional Hydrodynamics of a Janus Particle Vesicle

### 2022-03-30 doc/JFM2022/Final/main_jfm.tex
4.11 corrected
updates
3.8, 3.9 updated
\cdot
updated orcid link

\author{
Szu-Pei Fu\aff{1},
Bryan Quaife\aff{2},
Rolf Ryham\aff{1}, \and
Yuan-Nan Young\aff{3}
}
 \affiliation{
\aff{1}Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
 }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslets and rotlets centred at $\aa_i$
are
\begin{align}
\label{eq:stokeslet}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr| + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
    \label{eq:rotlet}
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet~\eqref{eq:stokeslet}  is torque-free
and has force $\FF_i$ while the rotlet~\eqref{eq:rotlet} is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, 
%and imposing that $\DD[\eeta]$ is force- and torque-free, 
%
the density function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \cdot \nnu \, \dif s &= 0, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta\times(\xx-\aa_i)^\perp \cdot \nnu \, \dif s &= 0,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = \frac{M}{\rho_0} \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by a parameter $k$, 
we can relate the scaled energy to that of the baseline case by 
\[E_k(x) = k(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_k$, and hence inter-particle separations, are independent to $k$.
The stretching modulus comes from $\frac{d^2E_k}{dx^2}$ and this 
quantity varies proportionally with $k$.

@@

\noindent
{\bf Author ORCIDs.}\\
\orcidlink{0000-0003-0140-1909} Szu-Pei Fu  {\url{https://orcid.org/0000-0003-0140-1909}}\\
\orcidlink{0000-0002-9186-8926} Bryan Quaife {\url{https://orcid.org/0000-0002-9186-8926}}\\  
\orcidlink{0000-0003-1626-7052} Rolf Ryham {\url{https://orcid.org/0000-0003-1626-7052}}\\  
\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480 }}

>>>>

\author{
Szu-Pei Fu\aff{1},
Bryan Quaife\aff{2},
Rolf Ryham\aff{1}, \and
Y.-N. Young\aff{3}
}
 \affiliation{
\aff{1}Department of Mathematics, \\Fordham University, Bronx, New York 10458, USA
\aff{2}Department of Scientific Computing, \\Florida State University, Tallahassee, Florida 32306, USA
\aff{3}Department of Mathematical Sciences, New Jersey Institute of Technology,\\ Newark, New Jersey 07102, USA
 }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility Problem Boundary Integral Equation}
Following previous work of~\cite{Lukas19}, we use the velocity
representation of~\cite{pow-mir1987}. In particular, we write the
velocity as the sum of a double-layer potential and $N_b$-many Stokeslets and
rotlets
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega.
\end{align}
The double-layer potential is
\begin{align}
  \DD[\eeta](\xx) = \frac{1}{\pi} \int_{\bd\Omega} 
    \frac{\rr \cdot \nnu}{|\rr|^2} \frac{\rr \otimes \rr}{|\rr|^2}
    \cdot \eeta(\yy) \, \dif s_\yy,
\end{align}
where $\rr = \xx - \yy$. The Stokeslets and rotlets centred at $\aa_i$
are
\begin{align}
\label{eq:stokeslet}
  \SS(\xx,\aa_i) \cdot \FF_i &= \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + 
    \frac{\rr \otimes \rr}{|\rr|^2}\right) \cdot \FF_i, \\
    \label{eq:rotlet}
  \RR(\xx,\aa_i) T_i &= \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2} T_i,
\end{align}
respectively, where $\rr = \xx - \aa_i$. The Stokeslet~\eqref{eq:stokeslet}  is torque-free
and has force $\FF_i$ while the rotlet~\eqref{eq:rotlet} is force-free and has torque
$T_i$. Therefore, the velocity~\eqref{eq:velocity} satisfies the total
force~\eqref{eq:force} and torque~\eqref{eq:torque} conditions if the
double-layer potential $\DD[\eeta]$ is force- and torque-free.  Matching
the limit of~\eqref{eq:velocity} with the rigid body motion, 
%and imposing that $\DD[\eeta]$ is force- and torque-free, 
%
the density function $\eeta$, translational velocity $\vv_i$, and angular velocity
$\omega_i$ satisfy
\begin{alignat}{3}
  \nonumber
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) \\
  \label{eq:SKIE}
    + \sum_{j=1}^{N_b} &
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),
    \quad &&\xx \in \Gamma_i,\: i=1,\ldots,N_b, \\
  \label{eq:mobility1}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, 
  &&i = 1,\ldots,N_b, \\
  \label{eq:mobility2}
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s &= T_i,
  &&i = 1,\ldots,N_b.
\end{alignat}

@@

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla \eta |^2 + \rho^{-1} \eta ^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P\left(\frac{|\tilde{\xx}_i - \tilde{\xx}_j|}{\rho_0}\right).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by a parameter $k$, 
we can relate the scaled energy to that of the baseline case by 
\[E_k(x) = k(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_k$, and hence inter-particle separations, are independent to $k$.
The stretching modulus comes from $\frac{d^2E_k}{dx^2}$ and this 
quantity varies proportionally with $k$.

@@

\noindent
{\bf Author ORCIDs.}\\
\orcidlink{0000-0003-0140-1909} Szu-Pei Fu  {\url{https://orcid.org/0000-0003-0140-1909}}\\
\orcidlink{0000-0002-9186-8926} Bryan Quaife {\url{https://orcid.org/0000-0002-9186-8926}}\\  
\orcidlink{0000-0003-1626-7052} Rolf Ryham {\url{https://orcid.org/0000-0003-1626-7052}}\\  
\orcidlink{0000-0001-9771-5480} Yuan-Nan Young  {\url{https://orcid.org/0000-0001-9771-5480}}
